Equations & R Code

### 2016-11-09 manuscript/coexistence-stability_ms.Rmd
udpates relative nonlinearity description

#### Implementing Relative Nonlinearity

\textcolor{red}{YOU NEED TO REMIND READERS ABOUT THE STANDARD RESOURCE COMPETITION MODELS, MACARTHUR, TILMAN, ETC. IN GENERAL, I THINK THIS PARAGRAPH NEEDS TO BE EXPANDED AND EXPLAINED MORE SLOWLY, STEP BY STEP.}

When considering consumer-resource dynamics, species coexistence by relative nonlinearity requires that each species has different nonlinear responses to resource availability, and resource availability must fluctuate through time.
In a constant resource environment, the species with the lowest $R^*$ will always exclude the other species. 
To create competitive hierarchies among species we manipulated species resource uptake curves such that the species with the lowest $R^*$ also had the lowest maximum growth rate at high resource levels (e.g., low *r*, low *a*, and low *b* values relative to other species in the Hill equation; Fig. SX).
Thus, our simulated species represent a continuum from resource-conservative to resource-acquisitive.
We still allow the germination rate ($\gamma$) to vary, but both species are perfectly correlated -- that is, $\rho=1$ (Fig. 1).

>>>>

#### Implementing Relative Nonlinearity
In the absence of environmental fluctuations, the outcome of competition between two species limited by the same resource is determined by the shape of their resource uptake curves.
That is, at constant resource supply, whichever species has the lowest resource requirement at equilibrium ($R^*$) will exclude all other species [@Tilman1982].
Resource fluctuations create opportunities for species coexistence because the resource level is then not fixed at the $R^*$ of the superior competitor.
If the resource uptake curves of each species are relatively nonlinear, then some species will be able to take advantage of resource levels that other species cannot [@Chesson1994].

For example, in Fig. 1C we show two species' resource uptake curves that are relatively nonlinear.
Species B has the lowest $R^*$ and would competitively exclude species A in the absence of environmental fluctuations.
But, fluctuating resource supplies can benefit species A because it can take advantage of relatively high resource levels due its higher saturation point.
Stable coexistence is only possible, however, if each species creates a disadvantage for itself when abundant.
This occurs in our model because when a resource conservative species (e.g., species B in Fig. 1C) is abundant, resource levels will remain high for a longer period of time because its draw down of resources starates.
Likwise, when a resource acquisative species (e.g., species A in Fig. 1C) is abundant it quickly draws down resources to levels that favor resource conservative species.
Such reciprocity ensures species can increase when rare and stablizes coexistence [@Armstrong1980; @Chesson2000; @Chesson2004].

### 2016-11-09 manuscript/coexistence-stability_ms.tex
udpates relative nonlinearity description

\textcolor{red}{YOU NEED TO REMIND READERS ABOUT THE STANDARD RESOURCE COMPETITION MODELS, MACARTHUR, TILMAN, ETC. IN GENERAL, I THINK THIS PARAGRAPH NEEDS TO BE EXPANDED AND EXPLAINED MORE SLOWLY, STEP BY STEP.}

When considering consumer-resource dynamics, species coexistence by
relative nonlinearity requires that each species has different nonlinear
responses to resource availability, and resource availability must
fluctuate through time. In a constant resource environment, the species
with the lowest \(R^*\) will always exclude the other species. To create
competitive hierarchies among species we manipulated species resource
uptake curves such that the species with the lowest \(R^*\) also had the
lowest maximum growth rate at high resource levels (e.g., low \emph{r},
low \emph{a}, and low \emph{b} values relative to other species in the
Hill equation; Fig. SX). Thus, our simulated species represent a
continuum from resource-conservative to resource-acquisitive. We still
allow the germination rate (\(\gamma\)) to vary, but both species are
perfectly correlated -- that is, \(\rho=1\) (Fig. 1).

@@

@@

>>>>

In the absence of environmental fluctuations, the outcome of competition
between two species limited by the same resource is determined by the
shape of their resource uptake curves. That is, at constant resource
supply, whichever species has the lowest resource requirement at
equilibrium (\(R^*\)) will exclude all other species (Tilman 1982).
Resource fluctuations create opportunities for species coexistence
because the resource level is then not fixed at the \(R^*\) of the
superior competitor. If the resource uptake curves of each species are
relatively nonlinear, then some species will be able to take advantage
of resource levels that other species cannot (Chesson 1994).

For example, in Fig. 1C we show two species' resource uptake curves that
are relatively nonlinear. Species B has the lowest \(R^*\) and would
competitively exclude species A in the absence of environmental
fluctuations. But, fluctuating resource supplies can benefit species A
because it can take advantage of relatively high resource levels due its
higher saturation point. Stable coexistence is only possible, however,
if each species creates a disadvantage for itself when abundant. This
occurs in our model because when a resource conservative species (e.g.,
species B in Fig. 1C) is abundant, resource levels will remain high for
a longer period of time because its draw down of resources starates.
Likwise, when a resource acquisative species (e.g., species A in Fig.
1C) is abundant it quickly draws down resources to levels that favor
resource conservative species. Such reciprocity ensures species can
increase when rare and stablizes coexistence (Armstrong and McGehee
1980, Chesson 2000a, Chesson et al. 2004).

@@

Armstrong, R. A., and R. McGehee. 1980. Competitive Exclusion. The
American Naturalist 115:151--170.

@@

Tilman, D. 1982. Resource competition and community structure. Pages
1--296.
